Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions

### 2022-12-19 latex/rosenbrock2d_convergence.tex
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Convergence Report For Rosenbrock Function}
\label{convergence:rosenbrock2d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &    74 &    26 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The convergence report for the Rosenbrock Function in 30 dimensions is shown in Table~\ref{convergence:rosenbrock2d}:

\begin{table}[H]
\centering
\caption{Convergence Report For Rosenbrock Function}
\label{convergence:rosenbrock2d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &    74 &    26 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

Except for DFP, Rosenbrock has good convergence for any algorithm for a constrained search space
of $\left[-1.5, 1.5\right]$. Although the Rosenbrock Function has only the global minimum in a
search space of $\left[-10, 10\right]$, it has a large banana shaped plateau near the optimal
solution, as it is shown in Section~\ref{isolinesrosenbrock2D}. The search space constraint serves
only to limit the number of iterations of each algorithm. The large search space tends to make the algorithm
walks too much to find the solution and tends to exceed the maximum iterations defined in the evaluation
criteria shown in Section~\ref{sec:introduction}.

### 2022-12-19 latex/rosenbrock2d_function_values.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{tabular}{lrrrr}
\toprule
Algorithm &      Minimal &      Maximum &         Mean &       Median \\
\midrule
      dfp & 1.135257e-20 & 1.330822e+00 & 3.883331e-02 & 1.008079e-13 \\
     bfgs & 1.232595e-30 & 5.420407e-20 & 1.520616e-21 & 3.568745e-24 \\
    lbfgs & 2.907107e-19 & 6.027957e-11 & 1.010571e-12 & 1.481586e-15 \\
      lma & 4.376780e-18 & 1.308671e-10 & 7.473415e-12 & 8.945853e-13 \\
\bottomrule
\end{tabular}

>>>>

The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rosenbrock2d}:

\begin{table}[H]
\centering
\caption{Statistical Information about function values For Rosenbrock Function}
\label{function_values:rosenbrock2d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &  Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 1.33 &  0.04 &    0.00 \\
 bfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
lbfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
  lma & 0.00 & 0.00 &  0.00 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

The values again are rounded. The median informs us that, for all
algorithms is expected to find the minimun of Rosenbrock Function.
Although the mean of DFP algorithm is greater than zero, it is expected
to converge more than diverge in the function constrained search space.

### 2022-12-19 latex/rosenbrock30d_best_fits.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{tabular}{llrrr}
\toprule
Algorithm &                                           Solution &  Iterations &  Function Evaluations &  Function Value \\
\midrule
      dfp & 1.000000001426901,1.0000000035108567,1.00000000... &        2767 &                  2790 &    2.303328e-14 \\
     bfgs & 1.0000000000000022,1.0,0.9999999999999846,0.999... &         207 &                   231 &    2.745279e-23 \\
    lbfgs & 1.0000000005707574,1.0000000006791032,1.0000000... &         160 &                   389 &    4.773145e-16 \\
      lma & 1.0,0.9999999999999999,0.9999999999999999,0.999... &          53 &                   131 &    1.018105e-16 \\
\bottomrule
\end{tabular}

>>>>

T
he best solutions of all algorithms for Rosenbrock Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:rosenbrock4d}:

\begin{table}[H]
\centering
\caption{Best Fits For Rosenbrock Function}
\label{solutions:rosenbrock30d}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &   2967 &     2990 &      0.00 \\
 bfgs & $S_{2}$ &    236 &      252 &      0.00 \\
lbfgs & $S_{3}$ &    164 &      406 &      0.00 \\
  lma & $S_{4}$ &     53 &      131 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

LMA is the less expensive algorithm to solve Rosenbrock Function in 30 dimensions, while DFP
is the most expensive of all.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/rosenbrock30d_convergence.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Convergence Report For Rosenbrock Function}
\label{convergence:rosenbrock2d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &    74 &    26 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The convergence report for the Rosenbrock Function in 30 dimensions is shown in Table~\ref{convergence:rosenbrock30d}:

\begin{table}[H]
\centering
\caption{Convergence Report For Rosenbrock Function}
\label{convergence:rosenbrock30d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &     1 &    99 &       0 &    100 \\
 bfgs &    80 &    20 &       0 &    100 \\
lbfgs &    95 &     5 &       0 &    100 \\
  lma &    88 &    12 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

DFP has poor convergence properties for the Rosenbrock Function with more than 2 dimensions.
The rest have quite the same profile regarding convergence. It is important to note that
although all algorithms does not converge for the presented initial solutions, it does not
diverge at all. Because of the stop criterion of all algorithms, which is the function gradient value,
and the banana shaped valley (plateau) that Rosenbrock function has, we have this behaviour.

### 2022-12-19 latex/rosenbrock30d_function_values.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{tabular}{lrrrr}
\toprule
Algorithm &      Minimal &   Maximum &      Mean &       Median \\
\midrule
      dfp & 2.303328e-14 & 29.257503 & 13.357326 & 1.307731e+01 \\
     bfgs & 2.745279e-23 &  3.986624 &  0.797325 & 6.316386e-22 \\
    lbfgs & 4.773145e-16 &  3.986624 &  0.199331 & 4.316852e-14 \\
      lma & 1.018105e-16 &  3.986624 &  0.478395 & 2.761710e-13 \\
\bottomrule
\end{tabular}

>>>>

The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rosenbrock30d}:

\begin{table}[H]
\centering
\caption{Statistical Information about function values For Rosenbrock Function}
\label{function_values:rosenbrock30d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &   Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 29.25 & 13.10 &   12.58 \\
 bfgs & 0.00 &  3.99 &  0.80 &    0.00 \\
lbfgs & 0.00 &  3.99 &  0.20 &    0.00 \\
  lma & 0.00 &  3.99 &  0.48 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

The median value informs us that all algorithms are like to find the solution
for Rosenbrock Function in 4 dimesions. The cases of poor convergence that all algorithms
have are reflected in the mean value. Looking at the Maximum value, it is noted that the mean value is
quite the same percentage shown in Table~\ref{convergence:rosenbrock30d}.

### 2022-12-19 latex/rosenbrock4d_best_fits.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{tabular}{llrrr}
\toprule
Algorithm &                                           Solution &  Iterations &  Function Evaluations &  Function Value \\
\midrule
      dfp & 0.9999999966340929,0.9999999907960823,0.9999999... &         292 &                   301 &    3.610838e-15 \\
     bfgs & 1.0000000000000053,1.0000000000000098,1.0000000... &          29 &                    35 &    6.042675e-28 \\
    lbfgs & 0.999999999931242,0.999999999845467,0.999999999... &          45 &                   134 &    1.861496e-19 \\
      lma & 0.9999999999421001,0.9999999998839636,0.9999999... &          18 &                    20 &    7.114597e-20 \\
\bottomrule
\end{tabular}

>>>>

The best solutions of all algorithms for Rosenbrock Function, obtained using the minimal
distance of the solution, are shown in Table~\ref{solutions:rosenbrock4d}:

\begin{table}[H]
\centering
\caption{Best Fits For Rosenbrock Function}
\label{solutions:rosenbrock4d}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &     44 &       49 &      0.00 \\
 bfgs & $S_{2}$ &     29 &       35 &      0.00 \\
lbfgs & $S_{3}$ &     45 &      134 &      0.00 \\
  lma & $S_{4}$ &     18 &       20 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

LMA is the less expensive algorithm to solve Rosenbrock Function in 4 dimensions, while LBFGS
is the most expensive of all. Although it has comparable iterations with DFP nd BFGS, it evaluates
the objective function twice as much of BFGS, the second most expensive algorithm.

Although the column F. Value points to the the same value, this is a rounded value
and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/rosenbrock4d_best_solutions.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Detailed Solutions For Rosenbrock Function}
\label{detailedsolutions:rosenbrock2d}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{2}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The best solutions of all algorithms for Rosenbrock Function, indicated as
$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rosenbrock4d}, are shown
in Table~\ref{detailedsolutions:rosenbrock4d}:

\begin{table}[H]
\centering
\caption{Detailed Solutions For Rosenbrock Function}
\label{detailedsolutions:rosenbrock4d}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{2}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{3}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{4}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
\bottomrule
\end{tabular}
\end{table}

The optimal point of Rosenbrock function in 4 dimensions is correctly pointed to $\left[1, 1, 1, 1\right]$. The Table~\ref{detailedsolutions:rosenbrock4d}
shows the same solution to all algorithms, because the values are so small and were rounded to fit on the Table. The differences of
the optimal point are of order $10^{-14}$ to $10^{-22}$, for the LMA, DFP, LBFGS and BFGS algorithms, respectively.

### 2022-12-19 latex/rosenbrock4d_convergence.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{table}
\centering
\caption{Convergence Report For Rosenbrock Function}
\label{convergence:rosenbrock30d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &     1 &    99 &       0 &    100 \\
 bfgs &    80 &    20 &       0 &    100 \\
lbfgs &    95 &     5 &       0 &    100 \\
  lma &    88 &    12 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

The convergence report for the Rosenbrock Function in 30 dimensions is shown in Table~\ref{convergence:rosenbrock4d}:

\begin{table}[H]
\centering
\caption{Convergence Report For Rosenbrock Function}
\label{convergence:rosenbrock4d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &    46 &    54 &       0 &    100 \\
 bfgs &    90 &    10 &       0 &    100 \\
lbfgs &    89 &    11 &       0 &    100 \\
  lma &    91 &     9 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

DFP has poor convergence properties for the Rosenbrock Function with more than 2 dimensions.
The rest have quite the same profile regarding convergence. It is important to note that
although all algorithms does not converge for the presented initial solutions, it does not
diverge at all. Because of the stop criterion of all algorithms, which is the function gradient value,
and the banana shaped valley (plateau) that Rosenbrock function has, we have this behaviour.

### 2022-12-19 latex/rosenbrock4d_function_values.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

\begin{tabular}{lrrrr}
\toprule
Algorithm &      Minimal &  Maximum &     Mean &       Median \\
\midrule
      dfp & 3.610838e-15 & 3.707671 & 0.601430 & 1.338231e-03 \\
     bfgs & 6.042675e-28 & 3.701429 & 0.370143 & 1.679398e-23 \\
    lbfgs & 1.861496e-19 & 3.701429 & 0.407157 & 2.624568e-15 \\
      lma & 7.114597e-20 & 3.701429 & 0.333129 & 1.322880e-13 \\
\bottomrule
\end{tabular}

>>>>

The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rosenbrock4d}:

\begin{table}[H]
\centering
\caption{Statistical Information about function values For Rosenbrock Function}
\label{function_values:rosenbrock4d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &  Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 3.71 &  0.60 &    0.00 \\
 bfgs & 0.00 & 3.70 &  0.37 &    0.00 \\
lbfgs & 0.00 & 3.70 &  0.41 &    0.00 \\
  lma & 0.00 & 3.70 &  0.33 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

The median value informs us that all algorithms are like to find the solution
for Rosenbrock Function in 4 dimesions. The cases of poor convergence that all algorithms
have are reflected in the mean value. Looking at the Maximum value, it is noted that the mean value is
quite the same percentage shown in Table~\ref{convergence:rosenbrock4d}.
